How does the writing system get informative? Differentiation or conservation?

### 2023-08-04 manuscript/wp4.tex
Add example from Irish

>>>>

Other languages

Irish orthography has special features to handle lenition and eclipsis. For example, when the word /pɑʃti/ (children) is eclipsed, it becomes /bɑʃti/ (the initial consonant is vocalized), but the spelling system retains the letter <p> in addition to adding a <b>: <páistí> becomes <bpáistí> under eclipsis. This allows the reader quick access to the root word from which the eclipsed form is derived and, in some cases, results in ambiguity avoidance (in this case, if the <p> were not retained, the spelling <báistí> would be confusible with the word for rain).
